### 2017-12-12 project/paper/paper.tex
Added files to repo

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

%\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

%\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
\usepackage{graphicx}
\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{times} % assumes new font selection scheme installed
\usepackage{mathtools} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{tikz}
\usepackage{tabulary}
\newcommand{\hvec}{\overset{\rightharpoonup}}
\newcommand{\argmin}{\arg\!\min}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\quotes}[1]{``#1''}
\usetikzlibrary{calc,positioning, fit, arrows}
%\usepackage{biber}

%for citing webcites
\usepackage{cite}
\usepackage{url}

\makeatletter
\newenvironment{tablehere}
  {\def\@captype{table}}
  {}

\newenvironment{figurehere}
  {\def\@captype{figure}}
  {}
\makeatother

\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\mat}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\transpose}{\ensuremath{\mathsf{T}}}
\newcommand{\of}[1]{\ensuremath{\left(#1\right)}}

\title{\LARGE \bf
Multi-dimensional Optimization of Gasoline-fueled Variable Pitch Multirotor Aircraft
}

\author{Dallin Briggs, Gary Ellingson% <-this % stops a space
%\thanks{$^{1}$James Jackson is a MS student in the Department of Mechanical Engineering, Brigham Young University
%        {\tt\small jamesjackson@byu.edu}}%
%\thanks{$^{2}$Gary Ellingson is a MS student in the Department of Mechanical Engineering, Brigham Young University
%        {\tt\small gary.ellingson@byu.edu}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

Currently, there are numerous multirotor unmanned aerial vehicles (UAVs) that are available to commercial operators and to consumers that are capable of lifting small payloads for an endurance of approximately 30 minutes or less. While these current multirotors are good for short endurance missions, there are few options for larger, higher payload capacity multirotors that are able to maintain flight for longer than an hour. This paper describes the optimization process used to develop a multirotor platform that maximizes the flight time of a gasoline-fueled multirotor UAV by varying several design variables related to the power required and the aerodynamics of the model.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

The creation of a multirotor aircaft capable of both carrying a relatively large payload and flying for a long duration would be very desirable for many applications.

Designing a gas powered multirotor aircraft requires several design decisions. When considering the total flight time of the aircraft, foremost of these design decisions are the choices of rotor, engine and gas tank size.  These design decisions along with several other aircraft parameters all have trade-offs that makes it difficult for a designer to simultaneously consider which design choice will allow for the longest flight time and/or greatest payload capacity.

This paper presents analysis and optimization methods for designing a gas powered multirotor aircraft.  The analysis focuses on modeling the engine and aerodynamic components with a limited consideration of aircraft structure.  These analyses are then used within multi-dimensional optimization to produce a vehicle design capable of both long duration flight and lifting heavy payloads.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{BACKGROUND}

Multirotor aircraft are useful for a variety of applications. This is because multirotors can hover, fly vertically, and fly horizontally. Further, they do not require landing strips and can carry sensor equipment for scientific or surveillance purposes. Multirotor use in package delivery is being considered by several large companies such as Google, Amazon and DHL \cite{Amazon2014}.

Incorporating a gas powered engine into a multirotor requires more then just exchanging the electric motors and batteries for an engine and a gas tank. The control of such a vehicle would also fundamentally change.  Electric multirotors are controlled by varying propeller rotational speed to produce varying thrust and torque, which in turn controls the attitude of the aircraft. Gas engines lack the ability to vary speed quickly enough to control the attitude of a multirotor aircraft. This means a fixed speed and variable pitch propeller is better suited for a gas powered vehicle.

Variable pitch mulitrotor aircraft are not as common as variable speed multirotors but they have been explored to some degree. Control of variable pitch multirotor aircraft was studied by Cutler, et al. \cite{Cutler2012}\cite{Cutler2012a} and Segui-Gasco, et al. \cite{Segui-Gasco2014}. There is a small, electric variable pitch quadcopter commercially available \cite{stingray2016} for performing stunts and inverted maneuvers.  There are also several hobbyist attempts at gas powered variable pitch quad-rotors (quads) \cite{diy2016}, \cite{hackaday2016}. In our knowledge there has been no attempt to use a gas powered variable pitch multirotor to maximize the flight time for carrying a relatively large payload for commercial applications.

There are many commercially available components that could be used to create a gas powered multirotor, including engines \cite{da2016} and variable pitch helicopter propellers \cite{align2016}. However, a gas powered multirotor would require a custom frame for mounting the engine and supplying power from the engine to the individual rotors.

Federal Aviation Administration (FAA) requirements \cite{faa2016} specify that model aircraft and UAVs of any sort must weigh less then 55 lbs (25 kg). UAVs or model aircraft weighing more than 55 lbs require special airworthiness certificates and are much more heavily regulated.

\section{MOTIVATION}

\begin{figure}
	\begin{center}
		\includegraphics[width=.5\textwidth]{current_capabilities.png}
		\caption{\textit{Graphic showing capabilities of current platforms and the goal of this project. The data points shown are specifications given by manufacturers of popular commercial and consumer UAVs and is collected from \cite{drones2016}.}} 
		\label{fig:current_cap}
	\end{center}
\end{figure}

Nearly all commercial and consumer multirotor UAVs are powered by lithium-polymer batteries because of their relatively high energy capacity to weight ratios. Although these batteries are very useful and reliable, they still offer much lower specific energy ratios than that of liquid fuels such as gasoline. The average specific energy for lithium-polymer batteries is approximately 0.95 MJ/kg \cite{Battuni2016}, where gasoline is 46.4 MJ/kg \cite{energyed2016}. This means that a gasoline-fueled multirotor can potentially fly much longer than a battery powered vehicle because it can carry more energy.

The goal of this project is to expand the flight envelope of multirotor aircraft.  Figure~\ref{fig:current_cap} demonstrates the current capabilities of consumer and commercial multirotors and depicts the goal of this project.  We believe that a multirotor that could carry larger payloads for longer periods of time would greatly expand the type and number of applications for these vehicles. A multirotor with this capability would also fundamentally change the way multirotors are used in commercial applications.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{METHODS}

Because the quad is going to be built using commercially available off-the-shelf components, the optimization must be closely based on a realistic model. Therefore, the analysis must either be based on observations from available hardware or attempt to analyze the hardware in its available configurations.  The following sections present some surrogate models for approximating engine parameters as well as an aerodynamic analysis of common variable pitch propellers.

\subsection{Engine}

The designer essentially can only choose the size of engine when choosing a power plant. All the other data about the engine (mass, maximum power, etc.) have to be functions of displacement size.  Data was collected for popular two stroke RC aircraft engines from several sources to produce the models for other unknown parameters. One source for engine data was Desert Aircraft \cite{da2016}.  Figure~\ref{fig:mass} shows the collected data for engine size and mass.  We performed a linear least squares best fit to produce a model for use in our analysis.

\begin{figure}
	\includegraphics[width=0.5\textwidth]{mass.png}
	\caption{The empirical data based surrogate model of engine mass as a function of displacement size. Data from desertaircraft.com \cite{da2016}. $\ y = ax + b \quad a = 0.02145 \quad b = 0.25412$}
		\label{fig:mass}
\end{figure}

Data was also used to produce a model of the power output of the engine as a function of size. Figure~\ref{fig:power} shows the collected data for engine size and power.  Again, we initially used a linear least squares fit to the data as well as compared our fit to data produced by Barnard Microsystems \cite{barnardmiro2016}. However, both models were inadequate for our analysis because they contain a non-zero y-intercept.  A non-zero y-intercept would allow an infinitely small engine to produce power and thus would allow the aircraft to have infinite flight time. To correct for this issue, we applied a quadratic fit to the data and forced it to intercept through the origin.

\begin{figure}
	\includegraphics[width=0.5\textwidth]{max_power.png}
	\caption{Empirical based surrogate model of engine maximum power as a function of displacement size. Notice the linear models have a non-zero y-intercept but the quadratic fit goes through the origin. Data from desertaircraft.com \cite{da2016} and barnardmicrosystems.com \cite{barnardmiro2016} $\ y = ax^2 + bx \quad a = -0.04548 \quad b = 79.504$}
		\label{fig:power}
\end{figure}

The engine efficiency was not modeled for this project and was assumed as a constant parameter.  Throughout the analysis, the shaft output power of the engine was 15\% of the power consumed from the fuel.

\subsection{Aerodynamics}

Much of the work done in the methodology of optimizing flight time was to find adequate models for the thrust, torque, and power required from the main rotor disks. Since each rotor will be designed using small-scale helicopter components that consist of variable-pitch rotors that have no twist, a simplified helicopter rotor aerodynamic model should be sufficient for these calculations.

Many of the existing aerodynamic models used in the aerospace industry to represent helicopter rotors are extremely complex and require specialized software tools (many of which are proprietary). High fidelity aerodynamic models generally require lots of computational power; so in order to focus on optimization methods, rather than the complex aerodynamic interactions of the system, several simplifications were made in analyzing the inflow angle and the down-wind air-rotor interactions of the propeller. Also, the model used assumes the multirotor is in hover, since that seems to be the primary use condition of multirotor aircraft.

Combined differential blade element and momentum theory for nonuniform inflow was used to calculate the thrust and the torque differentially across each rotor blade \cite{bramwell2001bramwell}. Using blade element theory, the differential thrust is given by

\begin{equation}
	dT_{prod} = \frac{1}{2} \rho a \Omega^2 r^2 (\theta - \phi) c \  dr,
	\label{thrust_eqn}
\end{equation}

where $\rho$ is the air density, \textit{a} is the lift-curve slope for the blade airfoil, $\Omega$ is the angular velocity of the rotors, \textit{r} is the radius of the annulus of the rotor being differentiated, $\theta$ is the blade pitch angle measured from the horizontal plane formed by the rotational disc of rotor blades, \textit{c} is the chord of the rotor, and $\phi = \tan^{-1}(U_p/U_T) $ is the inflow angle at the blade element. $U_P$ and $U_T$ are the components of air velocity relative to blade element perpendicular and tangential to the plane of rotation, respectively. The total thrust on each rotor is calculated by integrating equation \ref{thrust_eqn} across the rotor radius, \textit{R}. The total thrust for the multirotor, $T_{prod}$, can then be calculated by multiplying the rotor thrust by the number of \textit{N} rotors.

The differential torque for each rotor blade is given by

\begin{equation}
	dQ_{req} = \frac{1}{2} \rho \Omega^2 r^3 c (\delta + \phi C_L) \ dr,
	\label{torque_eqn}
\end{equation}

where $\delta$ is the local blade drag coefficient, and $C_L$ is the lift coefficient. The total torque for the multirotor , $Q_{req}$, can be found using the same method for calculating the total thrust.

The differential power produced by each rotor is then given by

\begin{equation}
	dP_{req} = dQ\Omega,
	\label{power_eqn}
\end{equation}

and the total power required by the rotors, $P_{req}$, can be calculated using the same method as total thrust and torque \cite{venkatesan2014fundamentals}.

Equations \ref{thrust_eqn}, \ref{torque_eqn} and \ref{power_eqn} are used in the constraints, as discussed in the optimization section. In practice, the thrust, torque, and power were integrated in a \textit{for loop} that divided each blade into 10 elements and then summed the differential values for each element. More divisions were made initially, but it greatly increased the computation time of the optimization algorithm and the results were approximately the same.

Since the goal of this project is to optimize the flight time of a multirotor and then build it using existing remote controlled aircraft components, a NACA 0012 airfoil (see \cite{abbott1959theory}) was used in the analysis for calculating the coefficient of lift, $C_L$, and the blade element drag coefficient, $\delta$. This airfoil approximately represents the airfoil of many commonly used remote control helicopters \cite{mettler2013identification}. Data points for this airfoil were generated using Xfoil, an aerodynamics tool developed by The Massachusetts Institute of Technology. This data was then fit with polynomials to approximately represent $C_L$ and $\delta$ across a range of the angles of attack, $\alpha$, continuously, where $\alpha = \theta - \phi$.

Momentum theory allows for a relatively simple calculation of the inflow angle for each element of the blade. This calculation is an approximation, but it is sufficient for our low-fidelity model in designing the rotor system. The inflow angle is given by

\begin{equation}
\phi^2 = (\frac{a\sigma}{8})(\theta-\phi),
\label{inflow_eqn}
\end{equation}

where

\[ \sigma = \frac{bc}{\pi r} \]

is the blade solidity ratio based on local rotor radius, and \textit{b} is the number of blades in each rotor.

\section{OPTIMIZATION}

Within the optimization there are two sets of design variables.  First, the design variables that influence the size of the vehicle: the rotor radius $R_{rot}$, the engine size $S_{eng}$, and the fuel capacity $f_{capacity}$.  Then, there are the design variables that are used to determine feasibility of the design: fuel burn rate $f_{rate}$, rotor pitch angle $\theta_{pitch}$, and propeller head speed $\omega_{rot}$. Number of blades per rotor and number of rotors were also initially treated as design variables. However, with the current aerodynamic model, the optimizer will create as many rotors with as many blades as possible to minimize the rotational speed required of each rotor to reduce the overall drag. Since adding more rotors would have un-modeled adverse affects on cost, complexity, and weight these variables are fixed as parameters in the analysis. Moving forward we will assume four sets of two blade rotors because this is a common configuration that would be reasonably simple to build. Finally, although the selection of off-the-shelf components is a fundamentally discrete choice, for simplification within the optimization each design variable is treated as a continuous variable.

We now setup the formal optimization problem
\begin{equation}
	\begin{split}
		min. & \quad f\of{x} = -t_{flight}\of{x} \\
		w.r.t. & \quad x = [R_{rot}, S_{eng}, f_{capacity}, f_{rate}, \theta_{pitch}, \omega_{rot}]^T \\
		s.t. & \quad cons\of{x} \leq 0 
	\end{split}
	\label{eq:objective}
\end{equation}

where flight time was calculated by 
\[
	t_{flight} = K_{energy}\frac{f_{capacity}}{f_{rate}}.
\]
Without constraints, the solution to maximizing flight time would be trivial to calculate as well as impossible to construct. Therefore to optimize the system we must use constraints that ensure the quad is feasible and legal, according to the FAA \cite{faa2016}. The constraints are on the power produced by the engine ($P_{shaft}$), power required by the rotors ($P_{rot}$), thrust produced by the rotors ($T_{prod}$), total weight of the vehicle ($W_{total}$) and maximum power capabilities of the engine ($P_{max}$). To use the constraints correctly, the following relationships must hold:

\[
	\begin{split}
	P_{rot} & \leq P_{shaft} \\
	W_{total} & \leq T_{prod} \\ 
	P_{shaft} & \leq P_{max} \\
	W_{total} & \leq 55 lbs
	\end{split}
\]

The above aerodynamic model is used to calculate $P_{rot}$ and $T_{prod}$. $P_{shaft}$ is calculated from the fuel burn rate and engine efficiency. $W_{total}$ is the combined weight of the engine, vehicle frame, fuel, and payload. $P_{max}$ comes from the surrogate engine power model depicted in figure~\ref{fig:power}.

The design variables were scaled for input in to the optimizer. The optimizers we used were the Matlab's \textit{fmincon} function using interior-point algorithm and the Python \textit{pyoptsparse} package using SNOPT algorithum. Gradients were found using automatic-differentiation in Matlab and finite-differencing in Python.

Our optimization algorithm found the maximum flight time given a payload, but another formulation would be to find the maximum payload given a specified flight time. This means we could create a Pareto frontier of this multi-objective optimization. However, to simplify we can create figure~\ref{fig:payload} by varying the payload parameter within our optimization (not a true Pareto frontier because payload was not specifically optimized). We then can further explore how the characteristics of a gas quad change as we optimize the flight time for different payloads. For example, figure~\ref{fig:eng_v_pl} shows how the optimal engine size changes as the payload parameter varies.

\begin{figure}
	\includegraphics[width=0.5\textwidth]{pareto_front.png}
	\caption{Pareto frontier-like curve found by optimizing for flight time given specified payloads.}
		\label{fig:payload}
\end{figure}

\begin{figure}
	\includegraphics[width=0.5\textwidth]{engine_size_vs_payload.png}
	\caption{Optimal engine size (cc) given a specified payload.}
		\label{fig:eng_v_pl}
\end{figure}

Because the final design requires a single optimal solution and not a range of solutions that depend on our payload capacity, we then simultaneously optimized at several payloads. This means the optimization must maximize the total combined flight time while satisfying constraints for operating points.

\section{RESULTS AND DISCUSSION}

When simultaneously optimizing with 3, 5, and 7~kg payloads our optimizer converges to an optimal solution. The solution flight time is at least 42.46~minutes with a payload not greater than 7~kg. The values of the optimal design variables can be seen in table~\ref{table:unbound_results}.

\begin{tablehere}
\centering
\vspace{5mm}
	\begin{tabulary}{0.5\textwidth}{|C|C|}
		\hline
		Design Variable & Optimal Value \\ \hline \hline
		Rotor radius (m) & 2.156 \\ \hline
		Engine size (cc) & 176.9 \\ \hline
		Fuel Capacity (kg) & 6.45 \\ \hline
		Fuel burn rate (g/s) & 1.898 \\ \hline
		Rotor pitch (deg) & 17.6 \\ \hline
		Head speed (rpm) & 135.1 \\ \hline
	\end{tabulary}
\caption{Optimal design variables for loosely bound constraints.}
\label{table:unbound_results}
\end{tablehere}

The above solution is a vehicle with unreasonably large, slow moving propellers. While bounding our rotor size would give a more physically manageable solution, it would have also meant our optimization was largely an aerodynamic analysis with a small optimization of engine size. Leaving the variable loosely bounded gives more insight about the trade-offs the vehicle makes for efficiency.

We also found that the solutions varied greatly with very small changes in our aerodynamic analysis. Personal experience with RC aircraft leads us to believe that the head speed and pitch angles are too extreme. Further validation of our analysis would be required before a design such as this were to be built.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{CONCLUSION}

We have demonstrated an optimization of a gas powered variable pitch multirotor aircraft capable of carrying relatively large payloads for long durations.  The optimization produced a design that is feasible according to our analysis.  The design can carry up to 7~kg for at least 42.5~minutes.  This result is far better then the current capability of battery powered vehicles on the market.

The optimization analysis makes several assumptions and approximations that would need to be improved in order to better trust the solution.  Furthermore, the optimization chose a design from a continuous space when only discrete off-the-shelf choices are available. Further selection of the components would be needed to build a quad through a discrete optimization algorithm or analyzing all designs close to the continuous optimum. Future work would also include using better aerodynamic modeling and validation with testing, adding structural analysis to find the weight of the frame, and optimizing under uncertainty due to inaccuracies in analysis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{APPENDIX}

% Appendixes should appear before the acknowledgment.

% \section*{ACKNOWLEDGMENT}

% Important people/organizations who made it possible

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{./library}
\bibliographystyle{ieeetr}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% SAVED STUFF

%new document

### 2017-12-12 project/target_classifier.py

@@ -1,0 +1,39 @@
+import numpy as np
+import tensorflow as tf
+import vgg16
+from scipy.misc import imread, imresize
+import time
+from tqdm import trange
+from scipy.misc import imsave
+import sqlite3
+
+def get_annotations(filename):
+    conn = sqlite3.connect(filename)
+    cur = conn.cursor()
+    cur.execute("SELECT * FROM bounding_boxes")
+    rows = cur.fetchall()
+    return rows
+
+
+def init_vgg(sess):
+    height = 200
+    width = 300
+    opt_img = tf.Variable( tf.truncated_normal( [1,height, width,3],
+                                            dtype=tf.float32,
+                                            stddev=1e-1), name='opt_img' )
+    tmp_img = tf.clip_by_value( opt_img, 0.0, 255.0 )
+    vgg = vgg16.vgg16(tmp_img, 'vgg16_weights.npz', sess)
+    return vgg
+
+
+sess = tf.Session()
+
+data_file = '/home/dallin/Dropbox/Deep_Learning/Project/Dataset_atrium/atrium_annotations/atrium_gt.sqlite'
+data = get_annotations(data_file)
+
+vgg = init_vgg(sess)
+
+
+
+print('hello')
+

### 2017-12-13 project/paper/paper.tex
Setup basic architecture

@@
 \title{\LARGE \bf
-Multi-dimensional Optimization of Gasoline-fueled Variable Pitch Multirotor Aircraft
+Vision Based Multiple Target Tracking Using Deep Learning and Recursive RANSAC
 }
 
-\author{Dallin Briggs, Gary Ellingson% <-this % stops a space
-%\thanks{$^{1}$James Jackson is a MS student in the Department of Mechanical Engineering, Brigham Young University
-%        {\tt\small jamesjackson@byu.edu}}%
-%\thanks{$^{2}$Gary Ellingson is a MS student in the Department of Mechanical Engineering, Brigham Young University
-%        {\tt\small gary.ellingson@byu.edu}}%
-}
+\author{Dallin Briggs}
 
@@
 
-Currently, there are numerous multirotor unmanned aerial vehicles (UAVs) that are available to commercial operators and to consumers that are capable of lifting small payloads for an endurance of approximately 30 minutes or less.
-While these current multirotors are good for short endurance missions, there are few options for larger, higher payload capacity multirotors that are able to maintain flight for longer than an hour.
-This paper describes the optimization process used to develop a multirotor platform that maximizes the flight time of a gasoline-fueled multirotor UAV by varying several design variables related to the power required and the aerodynamics of the model.
+This report describes the methods used to improve Visual MTT with Deep Learning.
 
@@
 
-The creation of a multirotor aircaft capable of both carrying a relatively large payload and flying for a long duration would be very desirable for many applications.
-
-Designing a gas powered multirotor aircraft requires several design decisions.
-When considering the total flight time of the aircraft, foremost of these design decisions are the choices of rotor, engine and gas tank size.
-These design decisions along with several other aircraft parameters all have trade-offs that makes it difficult for a designer to simultaneously consider which design choice will allow for the longest flight time and/or greatest payload capacity.
-
-This paper presents analysis and optimization methods for designing a gas powered multirotor aircraft.
-The analysis focuses on modeling the engine and aerodynamic components with a limited consideration of aircraft structure.
-These analyses are then used within multi-dimensional optimization to produce a vehicle design capable of both long duration flight and lifting heavy payloads.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Multirotor aircraft are useful for a variety of applications.
-This is because multirotors can hover, fly vertically, and fly horizontally.
-Further, they do not require landing strips and can carry sensor equipment for scientific or surveillance purposes.
-Multirotor use in package delivery is being considered by several large companies such as Google, Amazon and DHL \cite{Amazon2014}.
-
-Incorporating a gas powered engine into a multirotor requires more then just exchanging the electric motors and batteries for an engine and a gas tank.
-The control of such a vehicle would also fundamentally change.
-Electric multirotors are controlled by varying propeller rotational speed to produce varying thrust and torque, which in turn controls the attitude of the aircraft.
-Gas engines lack the ability to vary speed quickly enough to control the attitude of a multirotor aircraft.
-This means a fixed speed and variable pitch propeller is better suited for a gas powered vehicle.
-
-Variable pitch mulitrotor aircraft are not as common as variable speed multirotors but they have been explored to some degree.
-Control of variable pitch multirotor aircraft was studied by Cutler, et al.
-\cite{Cutler2012}\cite{Cutler2012a} and Segui-Gasco, et al.
-\cite{Segui-Gasco2014}.
-There is a small, electric variable pitch quadcopter commercially available \cite{stingray2016} for performing stunts and inverted maneuvers.
-There are also several hobbyist attempts at gas powered variable pitch quad-rotors (quads) \cite{diy2016}, \cite{hackaday2016}.
-In our knowledge there has been no attempt to use a gas powered variable pitch multirotor to maximize the flight time for carrying a relatively large payload for commercial applications.
-
-There are many commercially available components that could be used to create a gas powered multirotor, including engines \cite{da2016} and variable pitch helicopter propellers \cite{align2016}.
-However, a gas powered multirotor would require a custom frame for mounting the engine and supplying power from the engine to the individual rotors.
-
-Federal Aviation Administration (FAA) requirements \cite{faa2016} specify that model aircraft and UAVs of any sort must weigh less then 55 lbs (25 kg).
-UAVs or model aircraft weighing more than 55 lbs require special airworthiness certificates and are much more heavily regulated.
-
 \section{MOTIVATION}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=.5\textwidth]{current_capabilities.png}
-		\caption{\textit{Graphic showing capabilities of current platforms and the goal of this project.
-The data points shown are specifications given by manufacturers of popular commercial and consumer UAVs and is collected from \cite{drones2016}.}}
-		\label{fig:current_cap}
-	\end{center}
-\end{figure}
-
-Nearly all commercial and consumer multirotor UAVs are powered by lithium-polymer batteries because of their relatively high energy capacity to weight ratios.
-Although these batteries are very useful and reliable, they still offer much lower specific energy ratios than that of liquid fuels such as gasoline.
-The average specific energy for lithium-polymer batteries is approximately 0.95 MJ/kg \cite{Battuni2016}, where gasoline is 46.4 MJ/kg \cite{energyed2016}.
-This means that a gasoline-fueled multirotor can potentially fly much longer than a battery powered vehicle because it can carry more energy.
-
-The goal of this project is to expand the flight envelope of multirotor aircraft.
-Figure~\ref{fig:current_cap} demonstrates the current capabilities of consumer and commercial multirotors and depicts the goal of this project.
-We believe that a multirotor that could carry larger payloads for longer periods of time would greatly expand the type and number of applications for these vehicles.
-A multirotor with this capability would also fundamentally change the way multirotors are used in commercial applications.
 
@@
 
-Because the quad is going to be built using commercially available off-the-shelf components, the optimization must be closely based on a realistic model.
-Therefore, the analysis must either be based on observations from available hardware or attempt to analyze the hardware in its available configurations.
-The following sections present some surrogate models for approximating engine parameters as well as an aerodynamic analysis of common variable pitch propellers.
-
-\subsection{Engine}
-
-The designer essentially can only choose the size of engine when choosing a power plant.
-All the other data about the engine (mass, maximum power, etc.) have to be functions of displacement size.
-Data was collected for popular two stroke RC aircraft engines from several sources to produce the models for other unknown parameters.
-One source for engine data was Desert Aircraft \cite{da2016}.
-Figure~\ref{fig:mass} shows the collected data for engine size and mass.
-We performed a linear least squares best fit to produce a model for use in our analysis.
-
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{mass.png}
-	\caption{The empirical data based surrogate model of engine mass as a function of displacement size. Data from desertaircraft.com \cite{da2016}. $\ y = ax + b \quad a = 0.02145 \quad b = 0.25412$}
-		\label{fig:mass}
-\end{figure}
-
-Data was also used to produce a model of the power output of the engine as a function of size.
-Figure~\ref{fig:power} shows the collected data for engine size and power.
-Again, we initially used a linear least squares fit to the data as well as compared our fit to data produced by Barnard Microsystems \cite{barnardmiro2016}.
-However, both models were inadequate for our analysis because they contain a non-zero y-intercept.
-A non-zero y-intercept would allow an infinitely small engine to produce power and thus would allow the aircraft to have infinite flight time.
-To correct for this issue, we applied a quadratic fit to the data and forced it to intercept through the origin.
-
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{max_power.png}
-	\caption{Empirical based surrogate model of engine maximum power as a function of displacement size.
-Notice the linear models have a non-zero y-intercept but the quadratic fit goes through the origin.
-Data from desertaircraft.com \cite{da2016} and barnardmicrosystems.com \cite{barnardmiro2016} $\ y = ax^2 + bx \quad a = -0.04548 \quad b = 79.504$}
-		\label{fig:power}
-\end{figure}
-
-The engine efficiency was not modeled for this project and was assumed as a constant parameter.
-Throughout the analysis, the shaft output power of the engine was 15\% of the power consumed from the fuel.
-
-\subsection{Aerodynamics}
-
-Much of the work done in the methodology of optimizing flight time was to find adequate models for the thrust, torque, and power required from the main rotor disks.
-Since each rotor will be designed using small-scale helicopter components that consist of variable-pitch rotors that have no twist, a simplified helicopter rotor aerodynamic model should be sufficient for these calculations.
-
-Many of the existing aerodynamic models used in the aerospace industry to represent helicopter rotors are extremely complex and require specialized software tools (many of which are proprietary).
-High fidelity aerodynamic models generally require lots of computational power; so in order to focus on optimization methods, rather than the complex aerodynamic interactions of the system, several simplifications were made in analyzing the inflow angle and the down-wind air-rotor interactions of the propeller.
-Also, the model used assumes the multirotor is in hover, since that seems to be the primary use condition of multirotor aircraft.
-
-Combined differential blade element and momentum theory for nonuniform inflow was used to calculate the thrust and the torque differentially across each rotor blade \cite{bramwell2001bramwell}.
-Using blade element theory, the differential thrust is given by
-
-\begin{equation}
-	dT_{prod} = \frac{1}{2} \rho a \Omega^2 r^2 (\theta - \phi) c \  dr,
-	\label{thrust_eqn}
-\end{equation}
-
-where $\rho$ is the air density, \textit{a} is the lift-curve slope for the blade airfoil, $\Omega$ is the angular velocity of the rotors, \textit{r} is the radius of the annulus of the rotor being differentiated, $\theta$ is the blade pitch angle measured from the horizontal plane formed by the rotational disc of rotor blades, \textit{c} is the chord of the rotor, and $\phi = \tan^{-1}(U_p/U_T) $ is the inflow angle at the blade element.
-$U_P$ and $U_T$ are the components of air velocity relative to blade element perpendicular and tangential to the plane of rotation, respectively.
-The total thrust on each rotor is calculated by integrating equation \ref{thrust_eqn} across the rotor radius, \textit{R}.
-The total thrust for the multirotor, $T_{prod}$, can then be calculated by multiplying the rotor thrust by the number of \textit{N} rotors.
-
-The differential torque for each rotor blade is given by
-
-\begin{equation}
-	dQ_{req} = \frac{1}{2} \rho \Omega^2 r^3 c (\delta + \phi C_L) \ dr,
-	\label{torque_eqn}
-\end{equation}
-
-where $\delta$ is the local blade drag coefficient, and $C_L$ is the lift coefficient.
-The total torque for the multirotor , $Q_{req}$, can be found using the same method for calculating the total thrust.
-
-The differential power produced by each rotor is then given by
-
-\begin{equation}
-	dP_{req} = dQ\Omega,
-	\label{power_eqn}
-\end{equation}
-
-and the total power required by the rotors, $P_{req}$, can be calculated using the same method as total thrust and torque \cite{venkatesan2014fundamentals}.
-
-Equations \ref{thrust_eqn}, \ref{torque_eqn} and \ref{power_eqn} are used in the constraints, as discussed in the optimization section.
-In practice, the thrust, torque, and power were integrated in a \textit{for loop} that divided each blade into 10 elements and then summed the differential values for each element.
-More divisions were made initially, but it greatly increased the computation time of the optimization algorithm and the results were approximately the same.
-
-Since the goal of this project is to optimize the flight time of a multirotor and then build it using existing remote controlled aircraft components, a NACA 0012 airfoil (see \cite{abbott1959theory}) was used in the analysis for calculating the coefficient of lift, $C_L$, and the blade element drag coefficient, $\delta$.
-This airfoil approximately represents the airfoil of many commonly used remote control helicopters \cite{mettler2013identification}.
-Data points for this airfoil were generated using Xfoil, an aerodynamics tool developed by The Massachusetts Institute of Technology.
-This data was then fit with polynomials to approximately represent $C_L$ and $\delta$ across a range of the angles of attack, $\alpha$, continuously, where $\alpha = \theta - \phi$.
-
-Momentum theory allows for a relatively simple calculation of the inflow angle for each element of the blade.
-This calculation is an approximation, but it is sufficient for our low-fidelity model in designing the rotor system.
-The inflow angle is given by
-
-\begin{equation}
-\phi^2 = (\frac{a\sigma}{8})(\theta-\phi),
-\label{inflow_eqn}
-\end{equation}
-
-where
-
-\[ \sigma = \frac{bc}{\pi r} \]
-
-is the blade solidity ratio based on local rotor radius, and \textit{b} is the number of blades in each rotor.
-
-\section{OPTIMIZATION}
-
-Within the optimization there are two sets of design variables.
-First, the design variables that influence the size of the vehicle: the rotor radius $R_{rot}$, the engine size $S_{eng}$, and the fuel capacity $f_{capacity}$.
-Then, there are the design variables that are used to determine feasibility of the design: fuel burn rate $f_{rate}$, rotor pitch angle $\theta_{pitch}$, and propeller head speed $\omega_{rot}$.
-Number of blades per rotor and number of rotors were also initially treated as design variables.
-However, with the current aerodynamic model, the optimizer will create as many rotors with as many blades as possible to minimize the rotational speed required of each rotor to reduce the overall drag.
-Since adding more rotors would have un-modeled adverse affects on cost, complexity, and weight these variables are fixed as parameters in the analysis.
-Moving forward we will assume four sets of two blade rotors because this is a common configuration that would be reasonably simple to build.
-Finally, although the selection of off-the-shelf components is a fundamentally discrete choice, for simplification within the optimization each design variable is treated as a continuous variable.
-
-We now setup the formal optimization problem
-\begin{equation}
-	\begin{split}
-		min. & \quad f\of{x} = -t_{flight}\of{x} \\
-		w.r.t. & \quad x = [R_{rot}, S_{eng}, f_{capacity}, f_{rate}, \theta_{pitch}, \omega_{rot}]^T \\
-		s.t. & \quad cons\of{x} \leq 0 
-	\end{split}
-	\label{eq:objective}
-\end{equation}
-
-where flight time was calculated by 
-\[
-	t_{flight} = K_{energy}\frac{f_{capacity}}{f_{rate}}.
-\]
-Without constraints, the solution to maximizing flight time would be trivial to calculate as well as impossible to construct.
-Therefore to optimize the system we must use constraints that ensure the quad is feasible and legal, according to the FAA \cite{faa2016}.
-The constraints are on the power produced by the engine ($P_{shaft}$), power required by the rotors ($P_{rot}$), thrust produced by the rotors ($T_{prod}$), total weight of the vehicle ($W_{total}$) and maximum power capabilities of the engine ($P_{max}$).
-To use the constraints correctly, the following relationships must hold:
-
-\[
-	\begin{split}
-	P_{rot} & \leq P_{shaft} \\
-	W_{total} & \leq T_{prod} \\ 
-	P_{shaft} & \leq P_{max} \\
-	W_{total} & \leq 55 lbs
-	\end{split}
-\]
-
-The above aerodynamic model is used to calculate $P_{rot}$ and $T_{prod}$.
-$P_{shaft}$ is calculated from the fuel burn rate and engine efficiency.
-$W_{total}$ is the combined weight of the engine, vehicle frame, fuel, and payload.
-$P_{max}$ comes from the surrogate engine power model depicted in figure~\ref{fig:power}.
-
-The design variables were scaled for input in to the optimizer.
-The optimizers we used were the Matlab's \textit{fmincon} function using interior-point algorithm and the Python \textit{pyoptsparse} package using SNOPT algorithum.
-Gradients were found using automatic-differentiation in Matlab and finite-differencing in Python.
-
-Our optimization algorithm found the maximum flight time given a payload, but another formulation would be to find the maximum payload given a specified flight time.
-This means we could create a Pareto frontier of this multi-objective optimization.
-However, to simplify we can create figure~\ref{fig:payload} by varying the payload parameter within our optimization (not a true Pareto frontier because payload was not specifically optimized).
-We then can further explore how the characteristics of a gas quad change as we optimize the flight time for different payloads.
-For example, figure~\ref{fig:eng_v_pl} shows how the optimal engine size changes as the payload parameter varies.
-
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{pareto_front.png}
-	\caption{Pareto frontier-like curve found by optimizing for flight time given specified payloads.}
-		\label{fig:payload}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{engine_size_vs_payload.png}
-	\caption{Optimal engine size (cc) given a specified payload.}
-		\label{fig:eng_v_pl}
-\end{figure}
-
-Because the final design requires a single optimal solution and not a range of solutions that depend on our payload capacity, we then simultaneously optimized at several payloads.
-This means the optimization must maximize the total combined flight time while satisfying constraints for operating points.
-
 \section{RESULTS AND DISCUSSION}
-
-When simultaneously optimizing with 3, 5, and 7~kg payloads our optimizer converges to an optimal solution.
-The solution flight time is at least 42.46~minutes with a payload not greater than 7~kg.
-The values of the optimal design variables can be seen in table~\ref{table:unbound_results}.
-
-\begin{tablehere}
-\centering
-\vspace{5mm}
-	\begin{tabulary}{0.5\textwidth}{|C|C|}
-		\hline
-		Design Variable & Optimal Value \\ \hline \hline
-		Rotor radius (m) & 2.156 \\ \hline
-		Engine size (cc) & 176.9 \\ \hline
-		Fuel Capacity (kg) & 6.45 \\ \hline
-		Fuel burn rate (g/s) & 1.898 \\ \hline
-		Rotor pitch (deg) & 17.6 \\ \hline
-		Head speed (rpm) & 135.1 \\ \hline
-	\end{tabulary}
-\caption{Optimal design variables for loosely bound constraints.}
-\label{table:unbound_results}
-\end{tablehere}
-
-The above solution is a vehicle with unreasonably large, slow moving propellers.
-While bounding our rotor size would give a more physically manageable solution, it would have also meant our optimization was largely an aerodynamic analysis with a small optimization of engine size.
-Leaving the variable loosely bounded gives more insight about the trade-offs the vehicle makes for efficiency.
-
-We also found that the solutions varied greatly with very small changes in our aerodynamic analysis.
-Personal experience with RC aircraft leads us to believe that the head speed and pitch angles are too extreme.
-Further validation of our analysis would be required before a design such as this were to be built.
 
@@
 \section{CONCLUSION}
-
-We have demonstrated an optimization of a gas powered variable pitch multirotor aircraft capable of carrying relatively large payloads for long durations.
-The optimization produced a design that is feasible according to our analysis.
-The design can carry up to 7~kg for at least 42.5~minutes.
-This result is far better then the current capability of battery powered vehicles on the market.
-
-The optimization analysis makes several assumptions and approximations that would need to be improved in order to better trust the solution.
-Furthermore, the optimization chose a design from a continuous space when only discrete off-the-shelf choices are available.
-Further selection of the components would be needed to build a quad through a discrete optimization algorithm or analyzing all designs close to the continuous optimum.
-Future work would also include using better aerodynamic modeling and validation with testing, adding structural analysis to find the weight of the frame, and optimizing under uncertainty due to inaccuracies in analysis.
 

### 2017-12-13 project/target_classifier.py

@@ -22,18 +22,31 @@ def init_vgg(sess):
                                             dtype=tf.float32,
                                             stddev=1e-1), name='opt_img' )
     tmp_img = tf.clip_by_value( opt_img, 0.0, 255.0 )
-    vgg = vgg16.vgg16(tmp_img, 'vgg16_weights.npz', sess)
+    vgg = vgg16.vgg16(tmp_img, '/home/dallin/deep_learning_data/vgg_weights/vgg16_weights.npz', sess)
     return vgg
 
 
 sess = tf.Session()
 
-data_file = '/home/dallin/Dropbox/Deep_Learning/Project/Dataset_atrium/atrium_annotations/atrium_gt.sqlite'
+data_file = '/home/dallin/deep_learning_data/Dataset_atrium/atrium_annotations/atrium_gt.sqlite'
 data = get_annotations(data_file)
 
 vgg = init_vgg(sess)
 
+layers = [ 'conv1_1', 'conv1_2',
+           'conv2_1', 'conv2_2',
+           'conv3_1', 'conv3_2', 'conv3_3',
+           'conv4_1', 'conv4_2', 'conv4_3',
+           'conv5_1', 'conv5_2', 'conv5_3' ]
+conv_ops = [ getattr( vgg, x ) for x in layers ]
 
+# There are 52 target id's in the dataset.
+
+# TODO: Set bounding box to upper left corner and make it a fixed width and height.
+# TODO: Crop both the image and bgs image to the bounding box
+# TODO: If the target ID is new, then query the classification network if it has a high probability of being a known class.
+# TODO: If low probability, train on the image for 30 frames?
+# TODO: Setup classification and training network.
 
 print('hello')
 

### 2017-12-13 project/target_classifier.py
Added todo items

@@ -42,7 +42,13 @@ conv_ops = [ getattr( vgg, x ) for x in layers ]
 
 # There are 52 target id's in the dataset.
 
+# TODO: Bring in images, one at a time.
 # TODO: Set bounding box to upper left corner and make it a fixed width and height.
+# Average width is 75.6 pixels, median is 76
+# Average height is 170.3 pixels, median is 194.
+
+
+
 # TODO: Crop both the image and bgs image to the bounding box
 # TODO: If the target ID is new, then query the classification network if it has a high probability of being a known class.
 # TODO: If low probability, train on the image for 30 frames?

### 2017-12-20 project/paper/paper.tex
Finished with introductory stuff

@@
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
+\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this 
+%\documentclass{article}
 
@@
 \title{\LARGE \bf
-Vision Based Multiple Target Tracking Using Deep Learning and Recursive RANSAC
+Light Weight Vision Based Multiple Target Tracking Using Deep Learning and Recursive RANSAC
 }
@@
 
-This report describes the methods used to improve Visual MTT with Deep Learning.
+This report describes the methods used to improve the capabilities of Unmanned Aerial Vehicles in tracking targets autonomously on a lightweight, small platform that requires little computational resources.
+Unmanned aircraft are becoming increasingly more capable and smaller and the goal of this report is to show that a neural network can be effective in robustly tracking ground targets with small embedded single board computers on-board a small unmanned aircraft.
+This approach will be leveraging existing work done in this field (Recursive RANSAC) as the primary target tracker and neural networks to learn and classify targets.
+The target classification will be used in associating targets that are observed multiple times with previous tracks recorded by Recursive RANSAC.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{BACKGROUND}
+Multiple object tracking (MOT) is currently a popular topic in the deep learning community.
+It can be used for a variety of cases, but most are typically related to the robotics industry.
+Unmanned Aerial Vehicles (UAV's) have advanced rapidly in the past decade and are now being used for both military and commercial purposes.
+A common use case for UAV's in the military is for intelligence, surveillance, and reconnaissance (ISR) missions.
 
-\section{MOTIVATION}
+Currently, military UAV's are usually equipped with expensive gimballed cameras that are able to view targets such as people or vehicles from a high altitude.
+Those targets are being tracked by pilots who are remotely controlling the aircraft.
+This task can be difficult and time consuming for humans to track a target over the course of several hours.
+In order to improve the capabilities of UAV's to track ground targets autonomously, a neural network is proposed to learn targets and track them even after loosing visual line of sight temporarily.
+
+In this report, we will discuss the current capabilities of UAV's and where there exist technology gaps in their abilities to perform well in ISR missions.
+In section \ref{BACKGROUND}, we present the history and current work that has been done already to autonomously track ground targets from a ISR UAV.
+In this section, we will also discuss the importance of why a neural network could be useful in this application.
+Following this, in section \ref{METHODS}, our attempted methods to improve the existing capabilities with neural networks will be presented.
+The reader will then be able to read the results in \ref{RESULTS} and our final conclusion in \ref{CONCLUSION}.
+
+\subsection{SCOPE OF WORK}
+
+This project is not designed to create an end-to-end target tracking system using neural networks.
+That has already been done by several others already and it currently too computationally expensive to run on a small embedded computer.
+\textbf{The goal of this project is to integrate a neural network into the Visual Multi-Target Tracker (Visual MTT) that uses Recursive RANSAC to track targets.
+The roll of the neural network is to classify and identify the target when Visual MTT creates a new track.} With every new track Visual MTT creates, it will query the neural network and see if it has seen that target before.
+If it has, it Visual MTT will then associate this new target track with the old target track.
+The roll of a neural network in this system is illustrated in Figure \ref{fig:rransac}.
+
+Although the primary purpose of this project was to design a neural network around classifying target images, most of the time spent went towards collecting a good dataset to train and test on.
+Unfortunately, all of the data collected from actual flight tests and imagery at Brigham Young University wasn't able to be used because of the low quality of the images.
+Further details of this are discussed below.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=.45\textwidth]{gimbal_far.png}
+		\caption{\textit{This image shows the observed targets from a low-cost small UAV. As can be seen, the targets are difficult to observe and this makes them difficult to track.}} 
+		\label{fig:gimbal_far}
+	\end{center}
+\end{figure}
+
+\begin{figure*}
+	\begin{center}
+		\includegraphics[width=.85\textwidth]{rransac.png}
+		\caption{\textit{This block diagram shows how a neural network plays a roll in the Visual MTT framework. The scope of the work for this project is shown in green.}} 
+		\label{fig:rransac}
+	\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{BACKGROUND AND MOTIVATION} \label{BACKGROUND}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=.45\textwidth]{gimbal_zoomed.png}
+		\caption{\textit{This image shows the observed targets that has been digitally zoomed in on.}} 
+		\label{fig:gimbal_zoomed}
+	\end{center}
+\end{figure}
+
+In most use cases of military UAV's, ISR missions are primarily used to track ground targets that are of interest to the military.
+Receiving reliable intelligence about the ground target can be critical in saving the lives of many.
+Accurate information about what they are tracking and who they are tracking is extremely important because receiving wrong information can result in the undesirable consequence of the loss of innocent lives.
+Although current military UAV's are very capable in tracking ground targets, unfortunately, there are also many mistakes made and targets are lost.
+
+\begin{figure*}
+	\begin{center}
+		\includegraphics[width=.95\textwidth]{ssd.png}
+		\caption{\textit{The SSD network from \cite{liu2016ssd}. It is a modified version of the VGG-16 network.}} 
+		\label{fig:ssd}
+	\end{center}
+\end{figure*}
+
+Lost ground targets are the result of a couple of factors.
+The first factor is that when viewing a target from a high altitude and a far distance, the target can be blurred by distortions in the air or the target might be low resolution because the capabilities of the camera on-board the aircraft.
+An example of what a small UAV might observe from a lower-quality camera can be seen in Figure \ref{fig:gimbal_far}.
+To make matters worse, the resolution quickly degrades as the image is digitally zoomed on the target as can be seen in Figure \ref{fig:gimbal_zoomed}.
+This same problem exists for larger, more expensive military grade UAV's, but to a lesser degree.
+Often, however, the larger UAV's are observing the target from much farther away and at a higher altitude.
+
+The second factor in why targets are lost is because of human error.
+The military currently uses pilots/co-pilots to visually track the target on the ground using a video feed they receive back at their ground station.
+This video feed is subject to temporary glitches in the streaming service that can cause interruption of the video.
+Upon regaining the video feed, the gimballed camera may need to be realigned with the target.
+Given the image as observed in Figure \ref{fig:gimbal_far}, this may be difficult for a human operator to do if the scene is in a cluttered, pattern-like environment such as a city.
+The operator may not be able to visually recognize the desired target anymore.
+Human operators are also subject to boredom and fatigue when tracking a ground target for many hours.
+
+Work has been done to make target tracking autonomous and relatively robust.
+In \cite{niedfeldt2014multiple}, a method of tracking multiple targets using an algorithm called recursive random sample consensus (R-RANSAC) was developed at Brigham Young University for tracking multiple moving ground targets.
+This paper discusses the difficulties of tracking ground targets using computer vision methods because of noisy and spurious measurements, missed detections, and the interaction between multiple maneuvering targets.
+The method in \cite{niedfeldt2014multiple} presents a way to track moving targets by estimating their dynamic states using a Kalman filter.
+This is able to be done because of a linear acceleration model.
+R-RANSAC assumes that the target won't suddenly teleport or instantaneously stop or change directions.
+With this assumption, the Kalman filter can estimate and track the target by estimating the next state using the dynamics of a linear acceleration model.
+This method provides a great way to robustly track a continuously observed target that is constantly moving while being very computationally lightweight and efficient.
+
+R-RANSAC, however, is subject to some limitations.
+One of the primary limitations of R-RANSAC is that when a target is temporarily unobserved, ie.
+the target goes off the frame of the camera or the target moves behind an occlusion, the target is lost.
+The other main limitation with R-RANSAC is its inability to track static targets.
+If a target were to stop momentarily and then continue on, R-RANSAC would initialize a new track and make no correlation between the new track and the old one.
+It is the same case for when a target is temporarily blocked from the field of view.
+
+Work has also been done to improve R-RANSAC in \cite{ingersoll2015vision} and its data association problem.
+A Sequence Model (SM), which is a machine learner, is presented in \cite{ingersoll2015vision} to improve the data association from target tracks created by R-RANSAC.
+This is done by learning where the target location is in an inertial reference frame.
+This work greatly improved the ability for R-RANSAC to associate targets with previous target tracks by remembering where the target was last seen.
+However, error in measurements again still cause for lot of error to enter the system and often targets that were observed multiple times are often not associated with previous target tracks.
+Therefore, R-RANSAC still classifies them as new targets.
+
+There has also been numerous papers published about how neural networks could be used in target tracking.
+There are online decision making algorithms as presented in \cite{xiang2015learning} that uses Markov decision process to model the lifetime of an object.
+This method deserves further investigation with application to the problem discussed in this paper.
+However, it is unclear how computationally heavy this algorithm is.
+
+Other papers such as \cite{sadeghian2017tracking}, \cite{choi2015near}, and \cite{keuper2016multi} all present different methods on how do deal with tracking multiple targets.
+The methods presented in these papers, however, are all computationally too heavy for a small embedded computer on a small UAV.
+
+When only one object is observed, reinforcement learning can be a great approach such as in \cite{zhang2017deep}, \cite{choi2017visual}, \cite{yoo2017action}, and \cite{luo2017end}.
+These papers present much more computationally efficient ways to track a target; however, in the case of our problem where multiple targets are present, these solutions will not work.
+
+The most promising solutions for our problem are presented in \cite{liu2016ssd} and \cite{redmon2016you}.
+In \cite{liu2016ssd}, the single shot multibox detector (SSD) presents a very computationally efficient way of tracking multiple targets.
+The SSD network uses the VGG-16 as a base and convert two of the fully connected layers to convolutional layers, subsample parameters from those fully connected layers, and use the \textit{a trous} algorithm \cite{holschneider1990real} to fill in the gaps.
+The SSD network illustration from \cite{liu2016ssd} is shown in figure \ref{fig:ssd}.
+This network was chosen to be a base example for our problem because of its streamlined computational efficiency which even beat out YOLO from \cite{redmon2016you} as far as performance speed.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=.45\textwidth]{anaconda.jpg}
+		\caption{\textit{This is the Anaconda UAV. This aircraft is what we used to collect our data for this project. Its wingspan is 7 feet.}} 
+		\label{fig:anaconda}
+	\end{center}
+\end{figure}
+
+\section{DATA ANALYSIS} \label{DATA}
+
+\subsection{Data Collection}
+Most of the time spent for this project went towards collecting good data that we could use to train and test our network.
+Unfortunately, this process took way longer than expected.
+First, a set of data was collected from a small fixed-wing UAV so the results would be as real as possible.
+
+To simplify things, only two targets were present during the collection of the video data.
+This was intentionally the case to make the training and testing of the neural network much faster and simpler.
+We used the Anaconda UAV from ReadyMade RC products.
+This aircraft is capable of flying for an hour while carrying on-board a gimballed camera and an embedded computer.
+This aircraft can be seen in Figure \ref{fig:anaconda}.
+The camera we used was a low-cost global shutter camera called the PointGray Chameleon.
+It was on a two-axis gimbal mechanism that allowed the camera to pan and tilt.
+This camera setup can be seen in Figure \ref{fig:gimbal}.
+The images shown in \ref{fig:gimbal_far} and \ref{fig:gimbal_zoomed} are from this UAV and camera setup.
+The video was recorded on-board so we could test our neural network through several iterations.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=.45\textwidth]{gimbal.jpg}
+		\caption{\textit{This PointGrey Chameleon camera attached to a gimbal is what was used to collect the video data.}} 
+		\label{fig:gimbal}
+	\end{center}
+\end{figure}
+
+\subsection{DATA PRE-PROCESSING}
+
+After collecting the data, we needed a way to process the video data so that we could crop the image around the target and feed it to our neural network.
+This task, however, proved to be difficult.
+Originally, the plan was to use the work developed in our research group here at Brigham Young University in tracking the targets in the video.
+More work has been done to \cite{ingersoll2015vision} and \cite{niedfeldt2014multiple} to improve the tracking capabilities.
+The frame work in these papers has been modified and put into the Robot Operating System (ROS) framework.
+This new framework for tracking targets using R-RANSAC is called Visual Multi-Target Tracking (Visual MTT).
+The Visual MTT architecture is new research and has yet to be published in another paper.
+That publication is forthcoming.
+
+In attempting to use the Visual MTT algorithm to observe the moving targets, although it was fairly reliable in observing moving objects, it wasn't very reliable at predicting the center mass of the object in the image.
+This meant that when attempting to use the reference point given from the output of the Visual MTT framework as the center point where we should crop our image around to give to the neural network to train/classify, the cropped image often gave a result of the image from behind or in front of the target.
+This was difficult to debug and caused a lot of problems in trying to train our network since the network would train on images that were not the target most of the time.
+
+Another issue with using the data collected from the Anaconda UAV was that the cropped view of the targets had so little resolution that unless the target were wearing completely different colors, any difference between the targets was unobservable.
+This can be seen in Figure \ref{fig:gimbal_2}.
+This figure shows the second target that can be seen in \ref{fig:gimbal_far}.
+Therefore, this data was not going to work.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=.45\textwidth]{gimbal_zoomed_2.png}
+		\caption{\textit{This image shows a second target that has been digitally zoomed in on.}} 
+		\label{fig:gimbal_2}
+	\end{center}
+\end{figure}
+
+In order to progress faster with the development of the neural network, a video was recorded from on-top of the Joseph F.
+Smith Building at BYU.
+This video was recorded for another project prior to this project.
+The camera was set on a tripod and the video was still.
+This allowed for simple background subtraction to annotate the targets in the video.
+A resulting image from the annotated video can be seen in Figure \ref{fig:jfsb}.
+This provided much clearer targets as can be seen in Figure \ref{fig:jfsb_zoomed}.
+Even these images, however, were still not good enough for training a neural network.
+Although large color differences could be observed, several of the people were wearing similar colors.
+This made it nearly impossible for the network to distinguish one target from another.
+Another issue with this data set was that almost no targets would be obstructed at any time and then return to the line of sight.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=.45\textwidth]{jfsb.png}
+		\caption{\textit{This is a still image from video recorded from a stationary camera on top of a building.}} 
+		\label{fig:jfsb}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=.45\textwidth]{jfsb_zoomed.png}
+		\caption{\textit{This is a still image from video recorded from a stationary camera on top of a building.}} 
+		\label{fig:jfsb_zoomed}
+	\end{center}
+\end{figure}
+
+Ultimately, a dataset was found that has been made publicly available from \cite{jodoin2014urban}.
+We used the Atrium dataset from this paper.
+This dataset came with clear images of pedestrians walking around with different colored clothes.
+The background color, as can be seen in Figure \ref{fig:atrium_full} is also very different from the color of the pedestrian.
+This dataset also came with background subtracted images along with detailed annotations.
+These annotations and background subtracted images is what would be used in training and testing the neural network.
+It is worth noting that one of the time consuming parts of using this dataset was that the annotations and background subtracted images were indexed differently than the actual video image.
+This issue caused a massive delay in setting up the network.
+Using the annotations provided by the data set, each target image was cropped down a $60\times170$ pixel image from the center point of the annotation.
+This size was chosen because it was the median size for all of the annotations.
+Any target image that didn't meet this minimum size was not used in the training or testing of the neural network.
+The image size had to be of fixed width and height to easily pass into the VGG-16 network.
+The final result of the cropping can be seen in Figure \ref{fig:atrium_combined}.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=.45\textwidth]{atrium_full.png}
+		\caption{\textit{A still image from the Atrium dataset from \cite{jodoin2014urban}.}} 
+		\label{fig:atrium_full}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=.45\textwidth]{atrium_combined.png}
+		\caption{\textit{Cropped target image and matching background subtracted image. These images were used in the training of the network.}} 
+		\label{fig:atrium_combined}
+	\end{center}
+\end{figure}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{METHODS}
+\section{METHODS} \label{METHODS}
 
-\section{RESULTS AND DISCUSSION}
+In this section we will discuss the technical approach to creating a neural network to classify and identify targets.
+Much of the work so far in the project consisted of acquiring good data and preprocessing that data to provide reliable consistent images for the neural network to train on.
+Eventually the goal is to connect this neural network to the Visual MTT framework as shown in Figure \ref{fig:rransac}.
+In developing the neural network, however, the annotations provided in the dataset will be used in place of the Visual MTT framework.
+
+\subsection{Quantitative Metric}
+
+One of the benefits to using the Atrium dataset provided by \cite{jodoin2014urban} is that all targets visible in the video are annotated throughout the whole video.
+Each target, however, is assigned a new target identification each time the target disappears from the field of view and the reappears in the image frame.
+This allows us to easily test the neural network after training as if it is receiving a new track ID from Visual MTT.
+
+\section{RESULTS AND DISCUSSION} \label{RESULTS}
 
@@
 
-\section{CONCLUSION}
+\section{CONCLUSION} \label{CONCLUSION}
 

### 2017-12-20 project/target_classifier.py

@@ -2,10 +2,13 @@ import numpy as np
 import tensorflow as tf
 import vgg16
 from scipy.misc import imread, imresize
+import matplotlib.pyplot as plt
 import time
 from tqdm import trange
 from scipy.misc import imsave
 import sqlite3
+from scipy import ndimage
+
 
 def get_annotations(filename):
     conn = sqlite3.connect(filename)
@@ -15,23 +18,77 @@ def get_annotations(filename):
     return rows
 
 
-def init_vgg(sess):
-    height = 200
-    width = 300
-    opt_img = tf.Variable( tf.truncated_normal( [1,height, width,3],
+def init_vgg(sess, width, height):
+    opt_img = tf.Variable( tf.truncated_normal( [1,width, height, 3],
                                             dtype=tf.float32,
                                             stddev=1e-1), name='opt_img' )
     tmp_img = tf.clip_by_value( opt_img, 0.0, 255.0 )
     vgg = vgg16.vgg16(tmp_img, '/home/dallin/deep_learning_data/vgg_weights/vgg16_weights.npz', sess)
     return vgg
 
+def image_grabber(image_file):
+    image = imread(image_file)
+    return image
+
+def crop_image(image, data, width, height):
+    x1 = int(data[2])
+    y1 = int(data[3])
+    x2 = int(data[4])
+    y2 = int(data[5])
+    x = int((x1 + x2)/2) - int(width/2)
+    y = int((y1 + y2)/2) - int(height/2)
+    img_cropped = image[y:y+height, x:x+width]
+    return img_cropped
+
+
+# There are 53 target id's in the dataset.
+# Average width is 75.6 pixels, median is 76
+# Average height is 170.3 pixels, median is 194.
+
+def get_targets(i, data, width, height):
+    image_file = '/home/dallin/deep_learning_data/Dataset_atrium/atrium_frames/' + '%08d' % (i+1) + '.jpg'
+    bgs_file = '/home/dallin/deep_learning_data/Dataset_atrium/atrium_bgs/' + '%08d' % i + '.png'
+    targets = []
+    truths = []
+    if i in data[:,1]:
+        data_row = np.where(data[:,1] == i)
+        for j in range(0,len(data_row[0])):
+            data_index = data_row[0][j]
+            anno_h = int(data[data_index,5] - data[data_index,3])
+            anno_w = int(data[data_index,4] - data[data_index,2])
+            if anno_h >= height and anno_w >= width:
[…]

### 2017-12-20 project/paper/paper.tex
Paper almost done

@@
 %\documentclass{article}
-
+%\usepackage{nips10submit_e}
 %\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
@@
 \title{\LARGE \bf
-Light Weight Vision Based Multiple Target Tracking Using Deep Learning and Recursive RANSAC
+Lightweight Vision Based Multiple Target Tracking Using Deep Learning and Recursive RANSAC
 }
@@
 Another issue with this data set was that almost no targets would be obstructed at any time and then return to the line of sight.
+The dataset that was used in this project is discussed in section \ref{METHODS}.
 
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{METHODS} \label{METHODS}
+
+In this section we will discuss the technical approach to creating a neural network to classify and identify targets.
+Much of the work so far in the project consisted of acquiring good data and preprocessing that data to provide reliable consistent images for the neural network to train on.
+Eventually the goal is to connect this neural network to the Visual MTT framework as shown in Figure \ref{fig:rransac}.
+In developing the neural network, however, the annotations provided in the dataset will be used in place of the Visual MTT framework.
+
+\subsection{Quantitative Metric}
+
+One of the benefits to using the Atrium dataset provided by \cite{jodoin2014urban} is that all targets visible in the video are annotated throughout the whole video.
+Each target, however, is assigned a new target identification each time the target disappears from the field of view and the reappears in the image frame.
+This allows us to easily test the neural network after training as if it is receiving a new track ID from Visual MTT.
+To measure the accuracy, however, that had to be tracked by hand.
+This wasn't too difficult because there were only 7 individual people shown in the video.
+That meant that after the network saw the first 7 unique people, the rest of the track identifiers were repeats.
+This was measured by hand by pausing the program periodically and viewing the image in the video and the output of the neural network.
+A more scientific method could be derived if more time were permitted.
+
+\subsection{Data Preparation}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{METHODS} \label{METHODS}
+One trick that was use to improve results was that for each camera frame that came in, we made a copy of the horizontally flipped image.
+This allowed for the network to always train on at least two images at a time and not just over fit to each image as it comes in.
 
-In this section we will discuss the technical approach to creating a neural network to classify and identify targets.
-Much of the work so far in the project consisted of acquiring good data and preprocessing that data to provide reliable consistent images for the neural network to train on.
-Eventually the goal is to connect this neural network to the Visual MTT framework as shown in Figure \ref{fig:rransac}.
-In developing the neural network, however, the annotations provided in the dataset will be used in place of the Visual MTT framework.
+\begin{figure*}
+	\begin{center}
+		\includegraphics[width=.95\textwidth]{cnn.png}
+		\caption{\textit{This was the final network used in this project.}} 
+		\label{fig:cnn}
+	\end{center}
+\end{figure*}
 
-\subsection{Quantitative Metric}
+\subsection{Neural Network}
 
-One of the benefits to using the Atrium dataset provided by \cite{jodoin2014urban} is that all targets visible in the video are annotated throughout the whole video.
-Each target, however, is assigned a new target identification each time the target disappears from the field of view and the reappears in the image frame.
-This allows us to easily test the neural network after training as if it is receiving a new track ID from Visual MTT.
+The neural network that ended up being used in this report was a convolutional neural network (CNN) since the primary purpose of the network was a classification problem.
+In an attempt to make it robust and speedy, the first attempt at constructing a neural network was in following the SSD architecture given in \cite{liu2016ssd}.
+This architecture promised good results; however, we were unable to get this network to work.
+This was certainly a bug in the code.
+However, many hours were spent in trying to solve this problem and the problem persisted.
+
+The network that was ultimately used was the VGG-16 network through convolution 5-3.
+Then four fully connected layers were constructed with output sizes of 256, 128, 64, and 7, in that order.
+An illustration of this network can be seen in Figure \ref{fig:cnn}.
+This was a fairly traditional CNN.
+The primary way this CNN was unique was in the way data was passed to the CNN.
+With only one frame coming in at a time from a live video feed, this means that the network can only train on a few images at a time.
+When multiple targets were in the camera image, the network would be able to train on more than just one target.
+This caused several issues with feeding the network because the batch size was now a variable size.
+For this reason, I was unable to get the network to train.
 
 \section{RESULTS AND DISCUSSION} \label{RESULTS}
+
+Unfortunately, I was unable to get the network to train and classify the images.
+This is primarily because of the way a live video feed comes into the network.
+With traditional classification problems, training the network typically allows for passing in several images at a time in a batch.
+With a video streaming in, one target is viewed at a time.
+This can be problematic when training because the network can easily over fit for that one target.
+The other issue is that the network seems to need a variety of different classes to train against so that when it comes time to classify a target, it has multiple models to choose from.
+I have yet to come up with a way that tells the network when to train and when to start classifying.
+
+Although I was unable to get the network to train successfully, a lot was learned in the process of collecting and processing the image data.
+Ultimately, the goal of this project was to run a lightweight network that was computationally efficient enough to be implemented on our UAV's flight computer, an NVIDIA Jetson TX2, as shown in Figure \ref{fig:tx2}.
+Part of the reason why the images were so far cropped down was to improve the speed at which the network would run.
+Attempting to crop the image to a small size that just barely fit the target without some kind of truth, such as the annotations found in the Atrium dataset, proved to be a really difficult task.
+Relying on motion detection and the Visual MTT framework to provide a good center point for the target caused much hardship in trying to train a network.
+I learned that the Visual MTT framework may not be entirely suitable for the approach of cropping the image around the target and then sending that through a neural net to train on.
+A better approach for a neural network track recognition component for the MTT framework would be to implement something such as the SSD network on the full image.
+The computational resources of the TX2 flight computer could still be moderately conserved if the network only ran when Visual MTT picked up a new track.
+Further investigation into this will be done outside of the scope of this project.
+
+A significant amount of time was given in reviewing the literature for this project and it was found that the SSD network seemed most promising for multiple targets.
+It seemed that CNN's were the most common when it came to classifying multiple targets.
+Another approach to this problem, however, would be to use a recurrent neural network (RNN) for each single target that is tracked by the Visual MTT framework.
+RNN's are very good at tracking objects in motion and it could prove to be valuable when the targets are highly occluded.
+Perhaps even a joint CNN and RNN for detecting and tracking the target could be used as proposed in \cite{fangtrack}.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=.45\textwidth]{tx2.jpg}
+		\caption{\textit{The NVIDIA Jetson TX2 computer is used as an on-board flight computer. It has a low-power GPU that is capable of running lightweight neural networks.}} 
+		\label{fig:tx2}
+	\end{center}
+\end{figure}
 
@@
 \section{CONCLUSION} \label{CONCLUSION}
+
+This project was a difficult project.
+In total, I recorded at least 45 hours in researching, debugging, and writing.
+I spent the first 12 hours reading and researching different papers on how neural networks apply towards target tracking.
+Most of what I read about were neural networks that were very successful at tracking targets robustly, but were also very computationally heavy.
+Many of the algorithms presented in the references given were only able to run at a few frames per second on very expensive, heavy, and powerful graphics cards.
+While this works great for some ground based system, it is not feasible for small UAV's.
+
+The SSD network appears to be one of the fastest networks that is designed for tracking objects.
+For this reason, a modified version of it was selected to attempt to make a classification network for the Visual MTT process.
+Further debugging is required to get the network training on streaming video images coming into the network.
+
+A significant amount of time was also spent in collecting and processing data for the project.
+In total, approximately 23 hours were spent in this section of the project.
+The reason so much time was given to collecting the data was because we did not have any video data of multiple moving targets on the ground from a fixed-wing UAV.
+The video data that was collected for the purpose of this project will be useful for research in the BYU MAGICC lab in the future.
+After the first video data was found to be unusable for this project, the next dataset that was attempted was the video recorded from the top of the JFSB.
+Using background subtraction to extract a pseudo truth bounding box around moving targets also proved difficult for this project as the camera's auto-focus was often trying to refocus the camera.
+As a result, many of the bounding boxes around the targets had a lot of error and again it caused issues with training a neural network.
+Finally, the Atrium dataset was found and this was very useful.
+Indexing to the correct image with the correct bounding box for each target, however, also proved to be a very difficult task because of how the dataset was labeled.
+Learning how to deal with no targets in an image, to one or many targets in an image was also a useful experience.
+A lot of time was given to solving indexing issues here.
+
+The remainder 10 hours given to the project went into writing this report.
+Part of why so much effort was given to this report was in the hopes that in a few weeks when I get this network running with Visual MTT, we can actually submit a conference paper since this would be a unique contribution, especially to the community that is trying to track targets autonomously with small UAV's.
+
+Although the end result of the neural network is currently disappointing, I learned a lot in the process.
 

### 2017-12-20 project/target_classifier.py

@@ -79,6 +79,22 @@ def get_id(i, data):
     return id_nums
 
 
+def fc( x, out_size=50, is_output=False, name="fc" ):
+
+    with tf.variable_scope(name):
+        x_flat = tf.contrib.layers.flatten(x)
+        image_shape = x_flat.get_shape().as_list()
+        W = tf.get_variable(name='W', shape=[image_shape[-1], out_size], dtype=tf.float32,
+                            initializer=tf.contrib.layers.variance_scaling_initializer())
+        b = tf.get_variable(name='b', shape=[out_size], dtype=tf.float32,
+                            initializer=tf.contrib.layers.variance_scaling_initializer())
+        if is_output is False:
+            op = tf.identity(tf.nn.relu(tf.nn.bias_add(tf.matmul(x_flat, W), b), name='Relu'), name='output')
+        else:
+            op = tf.identity(tf.nn.bias_add(tf.matmul(x_flat, W), b), name='output')
+        return op
+
+
 height = 170
 width = 60
 
@@ -97,9 +113,31 @@ layers = [ 'conv1_1', 'conv1_2',
            'conv5_1', 'conv5_2', 'conv5_3' ]
 conv_ops = [ getattr( vgg, x ) for x in layers ]
 
+fc0 = fc(conv_ops[-1], out_size = 256, name='fc0')
+fc1 = fc(fc0, out_size = 128, name='fc1')
+fc2 = fc(fc1, out_size=64, name='fc2')
+fc3 = fc(fc2, out_size=14, is_output=True, name='fc3')
+
+y_t = tf.placeholder(dtype=tf.float32, shape=[None], name='true_label')
+
+loss = tf.reduce_mean(tf.nn.sparse_softmax_cross_entropy_with_logits(labels=y_t, logits=fc3))
+train_step = tf.train.AdamOptimizer(0.0001).minimize(loss)
+fc3_max = tf.arg_max(fc3, axis=1, output_type=tf.int32)
+
+loss_summary = tf.summary.scalar('loss', loss)
+
+timestamp = str(int(time.time()))
+writer = tf.summary.FileWriter("tensorboard/" + timestamp, sess.graph)
+sess.run(tf.global_variables_initializer())
+
+
 for i in range(0,4539):
     targets = get_targets(i, data, width, height)
     target_ids = get_id(i, data)
+    loss_sum = sess.run([loss_summary, train_step], feed_dict={y_t:target_ids})
[…]

### 2017-12-20 project/paper/paper.tex
Finished paper

@@
 
-Currently, military UAV's are usually equipped with expensive gimballed cameras that are able to view targets such as people or vehicles from a high altitude.
+Currently, military UAV's are usually equipped with expensive gimbaled cameras that are able to view targets such as people or vehicles from a high altitude.
 Those targets are being tracked by pilots who are remotely controlling the aircraft.
@@
 In this section, we will also discuss the importance of why a neural network could be useful in this application.
-Following this, in section \ref{METHODS}, our attempted methods to improve the existing capabilities with neural networks will be presented.
+Following section \ref{BACKGROUND}, in section \ref{METHODS}, our attempted methods to improve the existing capabilities with neural networks will be presented.
 The reader will then be able to read the results in \ref{RESULTS} and our final conclusion in \ref{CONCLUSION}.
@@
 \textbf{The goal of this project is to integrate a neural network into the Visual Multi-Target Tracker (Visual MTT) that uses Recursive RANSAC to track targets.
-The roll of the neural network is to classify and identify the target when Visual MTT creates a new track.} With every new track Visual MTT creates, it will query the neural network and see if it has seen that target before.
-If it has, it Visual MTT will then associate this new target track with the old target track.
+The role of the neural network is to classify and identify the target when Visual MTT creates a new track.} With every new track Visual MTT creates, it will query the neural network and see if it has seen that target before.
+If it has, Visual MTT will then associate this new target track with the old target track.
 The roll of a neural network in this system is illustrated in Figure \ref{fig:rransac}.
@@
 Although the primary purpose of this project was to design a neural network around classifying target images, most of the time spent went towards collecting a good dataset to train and test on.
-Unfortunately, all of the data collected from actual flight tests and imagery at Brigham Young University wasn't able to be used because of the low quality of the images.
+Unfortunately, all of the data collected from actual flight tests and imagery at Brigham Young University was not able to be used because of the low quality of the images.
 Further details of this are discussed below.
@@
 \end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 This video feed is subject to temporary glitches in the streaming service that can cause interruption of the video.
-Upon regaining the video feed, the gimballed camera may need to be realigned with the target.
+Upon regaining the video feed, the gimbaled camera may need to be realigned with the target.
 Given the image as observed in Figure \ref{fig:gimbal_far}, this may be difficult for a human operator to do if the scene is in a cluttered, pattern-like environment such as a city.
@@
 R-RANSAC, however, is subject to some limitations.
-One of the primary limitations of R-RANSAC is that when a target is temporarily unobserved, ie.
+One of the primary limitations of R-RANSAC is that when a target is temporarily unobserved, i.e.
 the target goes off the frame of the camera or the target moves behind an occlusion, the target is lost.
@@
 This was intentionally the case to make the training and testing of the neural network much faster and simpler.
-We used the Anaconda UAV from ReadyMade RC products.
-This aircraft is capable of flying for an hour while carrying on-board a gimballed camera and an embedded computer.
+We used the Anaconda UAV from Ready Made RC products.
+This aircraft is capable of flying for an hour while carrying on-board a gimbaled camera and an embedded computer.
 This aircraft can be seen in Figure \ref{fig:anaconda}.
-The camera we used was a low-cost global shutter camera called the PointGray Chameleon.
+The camera we used was a low-cost global shutter camera called the Point Gray Chameleon.
 It was on a two-axis gimbal mechanism that allowed the camera to pan and tilt.
@@
 		\includegraphics[width=.45\textwidth]{gimbal.jpg}
-		\caption{\textit{This PointGrey Chameleon camera attached to a gimbal is what was used to collect the video data.}} 
+		\caption{\textit{This Point Grey Chameleon camera attached to a gimbal is what was used to collect the video data.}} 
 		\label{fig:gimbal}
@@
 For this reason, I was unable to get the network to train.
+The loss function was the sparse softmax cross entropy between the label and the fourth fully connected layer.
 
@@
 Although the end result of the neural network is currently disappointing, I learned a lot in the process.
+One of the core concepts I learned was to start with the most simplified data you can possibly start with.
+Several hours would have been save had I found the Atrium dataset at the beginning of the project.
+I also learned a lot about the current capabilities of neural networks in detecting and classifying objects.
+This has been valuable research for my thesis work as I am attempting to track multiple targets from a small UAV.
+The research done for this project will be continued on over the next several weeks to possibly make a more robust target tracker.
 
